A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-09-24 manuscript.Rmd
mention zenondo directly closes #60

GitHub allows you to archive and label a specific version of your repository in the form of a release. A release tags a particular commit with an arbitrary label, e.g., as "submission,"[^sub] "preprint," or "published," and archives also "binary" products of your code, e.g. the resulting pdf of the manuscript or the docker image (see [Containerization]). From such a release a DOI can be created, making it easier to reference it (see this [GitHub Guide](https://guides.github.com/activities/citable-code/)[^doi]).

>>>>

GitHub allows you to archive and label a specific version of your repository in the form of a release. A release tags a particular commit with an arbitrary label, e.g., as "submission,"[^sub] "preprint," or "published," and archives also "binary" products of your code, e.g. the resulting pdf of the manuscript or the docker image (see [Containerization]). From such a release [zenodo.org](https://zenodo.org) can create a DOI, making it easier to reference it (see this [GitHub Guide](https://guides.github.com/activities/citable-code/)[^doi]).
